Soybean herbicide study - Dan Smith

### 2020-11-11 soyherb.Rmd
a

```{r }
lsmeans_14<- emmeans(model_14_2, ~ herbicide, cont="pairwise", adjust="none", type="response", alpha=0.05)
```

@@

>>>>

```{r }
lsmeans_14 <- emmeans(model_14_2, ~ herbicide, cont="pairwise", adjust="none", type="response", alpha=0.05)
```

@@

```{r}
nd14 <- data.frame(lsmeans_14$emmeans) %>% 
  mutate(dat = "14 DAT")
nd28 <- data.frame(lsmeans_28$emmeans)  %>% 
  mutate(dat = "28 DAT")
nd <- bind_rows(nd14, nd28)

nd %>% 
  mutate(herbicide = fct_relevel(herbicide, c("PRE fb glufosinate",
                    "PRE fb glufosinate + acetochlor",
                    "PRE fb glufosinate + dimethenamid-P",
                    "PRE fb glufosinate + S-metolachlor",
                    "PRE fb glufosinate + imazethapyr",
                    "PRE fb glufosinate + fomesafen",
                    "PRE fb glufosinate + pyroxasulfone",
                    "PRE fb glufosinate + fomesafen + acetochlor",
                    "PRE fb glufosinate + fomesafen + S-metolachlor"))) %>%
ggplot(aes(x=herbicide, response, y=response*100)) + 
  facet_wrap(~dat) +
  coord_flip() + 
  geom_point(size=3, color="#282728") + 
  theme_bw() +  
  labs(y="Waterhemp control (%)", x="", title="") +
  geom_errorbar(aes(ymin  =  lower.CL*100, ymax  =  upper.CL*100), width =  0.3, size  =  1, color="#282728") + 
  theme(axis.title = element_text(size=20, color="#282728", face="bold"), 
        axis.text.x = element_text(size=18, angle=0, hjust=1,
                                   color="#282728"), 
        axis.text.y = element_text(size=18, color="#282728"),
        plot.title = element_text(size=30, face="bold", hjust = 1, 
                                    color="#c5050c"), 
        strip.text = element_text(size=25, face="bold", color="#282728"),          strip.background =element_rect(fill="#dadfe1")) + 
  geom_hline(yintercept=90, linetype="dashed", color="#c5050c", size=1.2, show.legend = TRUE) +
  ylim(0,100) +
  ggsave("Figure2.pdf", width=18, height=9, dpi=600)
```
